Coherent optical association of a single molecule

### 2020-10-20 paper.tex
White space, remove duplicated reference entry, regenerate PDF
Clean up, breaking up long lines, remove molecule linetime from introduction

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
  and lifetime up to $1 \mathrm{ms}$ \textcolor{blue}{(1~ms seems long here)} with more than $60\%$ of the molecule created in the
  motional ground state.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning. 
%(We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image. We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer. In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

@@

% From these fits, we extract the 2 photon resonance frequency, Raman Rabi frequency, atomic lifetime and molecular lifetime.
%Each of these quantities provide us with information about a different combination of physical processes and the detuning dependency of them allows us to distinguish the contribution from the $v'=0$ excited states and other states.

First we look at the change in resonance frequency. As a function of the tweezer power, we observe the expected linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A). When we vary the tweezer frequency around the $v'=0$ intermediate state, we can further observe a $1/\Delta$ component and a constant background in the experimentally explored region. The background is caused by coupling to other excited states that are further away in energy. The $1/\Delta$ component, however, is due to the coupling between the molecular state and the $v'=0$ intermediate state. From this measurement, we can calculate a  $\Omega_m$ of $2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or $2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

@@

With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory, we now consider the background effects from other states with larger single photon detuning. Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency for a single photon detuning that is red of the $ v' = 0 $ and reduces it by about $30\%$ at the current detuning. However, this difference is not enough to explain the over factor of 10 discrepancy present in the experiment.
The same offset will increase the Rabi frequency for blue detuning, but we have observed additional excited states at slightly higher frequencies which prevent the blue side of the transition to be usable for the Raman transition.

These results suggest that the decoherence or loss we observed during the the Raman transition comes from either a higher than expected background scattering rate or a different intrinsic or technical source that we have not accounted for. We have observed a significant decrease in the coherence time without the ASE filter, suggesting the spectral purity of the laser is a significant source of scattering. Another source of decoherence could result from fluctuations in the power ratio between the two beams resulting in a fluctuation in the resonance position. In the experiment, we only stabilize the total power of the tweezer.

Lastly, to confirm that the excess scattering does not come from the atomic state, we measure the two-body scattering rate without turning on the second frequency (Fig.~\ref{f-det}C). The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent with a single photon scattering process. We have not been able to observe a dependency on the detuning in order to verify if the scattering process is related to the $v'=0$ state, but the power scaling strongly suggests the existence of a unknown two photon scattering process. Nevertheless, the absolute scattering rate is much lower than the total scattering rate and is not the limiting factor in our experiment. 
% Although we have good control on the total power of the tweezer and Raman beam to stabilizethe light shift on the transition, the power ratio of the two frequencies within the beam is not yet controlled as tightly and may result in a residual resonance fluctuation.

%%%% Maybe this following section about the B field can be relegated to a figure caption?
% Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
B field dependency $42.17(24) kHz/G$ which agrees with theory prediction of $... kHz/G$.

@@

>>>>

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
  with more than $60\%$ of the molecule created in the motional ground state.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image. We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer. In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

@@

First we look at the change in resonance frequency.
As a function of the tweezer power,
we observe the expected linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can calculate a $\Omega_m$ of
$2\pi\times36.162(20) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ or
$2\pi\times140.056(78) ~\mathrm{MHz}$ for the $15 ~\mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

@@

With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
we now consider the background effects from other states with larger single photon detuning.
Unfortunately, the background in the Raman Rabi frequency fit cancels the Rabi frequency
for a single photon detuning that is red of the $ v' = 0 $
and reduces it by about $30\%$ at the current detuning.
However, this difference is not enough to explain the over factor of $10$ discrepancy
present in the experiment.
The same offset will increase the Rabi frequency for blue detuning,
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usable for the Raman transition.

These results suggest that the decoherence or loss we observed during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source that we have not accounted for.
We have observed a significant decrease in the coherence time without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Another source of decoherence could result from fluctuations in the power ratio
between the two beams resulting in a fluctuation in the resonance position.
In the experiment, we only stabilize the total power of the tweezer.

Lastly, to confirm that the excess scattering does not come from the atomic state,
we measure the two-body scattering rate
without turning on the second frequency (Fig.~\ref{f-det}C).
The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
with a single photon scattering process.
We have not been able to observe a dependency on the detuning in order to verify
if the scattering process is related to the $v'=0$ state,
but the power scaling strongly suggests the existence of a unknown two photon scattering process.
Nevertheless, the absolute scattering rate is much lower than the total scattering rate
and is not the limiting factor in our experiment.

%%%% Maybe this following section about the B field can be relegated to a figure caption?
% Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
B field dependency $42.17(24) kHz/G$.

@@

% Fig2 make vertical remove 2C
% Bigger dots
